Report and Figures

### 2016-10-06 5_figs.Rmd
merge prep

cache %>%
	ggplot(aes(x = I_XY, y = J_XY)) + 
	geom_point(color = 'grey') + 
	theme_light() + 
	ylab(expression(J(X,Y))) + 
	xlab(expression(I(X,Y))) + 
	ggtitle('Mutual information and mean local information in major US cities') +
	geom_point(data = highlight, color = 'firebrick') + 
	geom_text_repel(data = highlight, aes(label = city))

ggsave('figs/mutual_fisher.pdf', width = 10, height = 6)

@@

  ggsave(paste0('figs/', city, '_percent_black.pdf'), width = 10, height = 10, units = 'cm')

@@

  stuff$grid %>% 
    fortify(region = 'id') %>% 
    left_join(stuff$grid@data[,c('id', 'pop', 'info')], by = c('id' = 'id')) %>% 
    ggplot(aes(x = long, y = lat, fill =  info, group = group)) + 
    geom_polygon() + 
    viridis::scale_fill_viridis(name = expression(J[Y](x))) + 
    ggthemes::theme_map() +
    ggtitle(city) + 
    theme(legend.justification=c(0,0), legend.position=c(.7,0),
          legend.title = element_text(size = 8)) + 
    theme(plot.title = element_text(size=10, 
                                  vjust=1))

  # paste0('figs/', city, '_grid.pdf')
  ggsave(paste0('figs/', city, '_grid.pdf'), width = 10, height = 10, units = 'cm')

@@

>>>>

cache %>%
	ggplot(aes(x = I_XY, y = J_XY)) + 
	geom_point(color = 'grey') + 
	theme_light() + 
	ylab(expression(J(X,Y))) + 
	xlab(expression(I(X,Y))) + 
	# ggtitle('Mutual information and mean local information in major US cities') +
	geom_point(data = highlight, color = 'firebrick') + 
	geom_text_repel(data = highlight, aes(label = city)) + 
  theme(legend.title = element_text(size = 8),
        plot.title = element_text(size=10, vjust=1))

ggsave('figs/mutual_fisher.pdf', width = 7, height = 4)

@@

  ggsave(paste0('figs/', city, '_percent_black.pdf'), width = 7, height = 7, units = 'cm')

@@

  stuff$grid %>% 
    fortify(region = 'id') %>% 
    left_join(stuff$grid@data[,c('id', 'pop', 'info')], by = c('id' = 'id')) %>% 
    ggplot(aes(x = long, y = lat, fill =  info, group = group)) + 
    geom_polygon() + 
    viridis::scale_fill_viridis(name = expression(J[Y](x)), limits = c(0, .5)) + 
    ggthemes::theme_map() +
    ggtitle(city) + 
    theme(legend.justification=c(0,0), legend.position=c(.7,0),
          legend.title = element_text(size = 8),
          plot.title = element_text(size=10, vjust=1))

  # paste0('figs/', city, '_grid.pdf')
  ggsave(paste0('figs/', city, '_grid.pdf'), width = 7, height = 7, units = 'cm')

@@

tab %>% mutate(percent_black = percent_black * 100)
